Estimation of Intracortical Connectivity in a Dynamical Neural Field Model

### 2010-06-23 ltx/PLoS/LaTeX_Manuscript.tex
edits to the tables

\begin{table}[!ht]
\caption{
\bf{Notation and Parameters}}
\begin{tabular}{|c|c|}
	\hline
\multicolumn{2}{|c|}{\textbf{Domain and indices}}\\
\hline
$\Omega$ & spatial domain \\
$t$ & time (seconds) \\
$\mathbf{r}$ & spatial location \\
$n$ & sensor index $n=1,..,N$ \\
$T$ & time step
\end{tabular}
\begin{flushleft}Table caption
\end{flushleft}
\label{tab:label}
\end{table}

% ~~~~~~~~~~~~~~~~~~~~
\begin{table}[h!]\footnotesize
    \begin{tabular}{ll}
        $\Omega$ & spatial domain \\
	    $t$ & time (seconds) \\
    	$\mathbf{r}$ & spatial location \\
	    $n$ & sensor index $n=1,..,N$ \\
    	$T$ & time step
    \end{tabular}
    \caption{Domain and indices}
\end{table}

% \begin{table}[h!]\footnotesize
%     \begin{tabular}{ll}
%         $y(\mathbf{r}_n,t)$ & observation \\
% 	    $v(\mathbf{r},t)$ & mean membrane potential \\
%     	$g(\mathbf{r},t)$ & average action potential rate \\
%     	$f(\mathbf{r},t)$ & firing function rate \\
%     	$e(\mathbf{r},t)$ & field disturbance, covariance $\gamma$\\
% 	$\epsilon(\mathbf{r}_n,t)$ & observation noise, covariance$\Sigma_\epsilon$ \\
%     \end{tabular}
%     \caption{Spatiotemporal Signals}
% \end{table}
% 
% \begin{table}[h!]\footnotesize
%     \begin{tabular}{ll}
%         	$h(t)$ & post-synaptic response kernel \\
% 	$m(\mathbf{r},\mathbf{r}')$ & sensor kernel, width $\sigma_m^2$ \\
% 	$\eta(t)$ & Heaviside function \\
% 	$\zeta$ & inverse synaptic time constant \\
% 	$w(\mathbf{r},\mathbf{r}')$ & spatial connectivity kernel \\
% 	$f_{max}$ & maximal firing rate \\
% 	$\varsigma$ & slope of sigmoidal activation function \\
% 	$v_0$ & firing threshold \\
% 	$\delta(t)$ & Dirac-delta function \\
% 	$D$ & Temporal differential operator \\
% 	$\xi$ & time constant parameter
%     \end{tabular}
%     \caption{Model}
% \end{table}
% 
% \begin{table}[h!]\footnotesize
%     \begin{tabular}{ll}
%         $L$ & number of field basis functions  \\
%     	$\mathbf{\phi(r)}$ & vector of Gaussian basis functions \\
%     	$\mathbf{x}_t$ & state vector at time $t$ \\
%     	$\mathbf{\psi}$ & vector of connectivity kernel basis functions \\
%     	$\theta$ & vector of connectivity kernel parameters \\
%     	$\Gamma$ & inner product of field basis functions \\
%     	$q()$ & state function \\
%     	$Q()$ & state function \\
% 	$\gamma(\mathbf r-\mathbf r')$& field disturbance covariance function\\
%     	$\mathbf{e}_t$ & state disturbance \\
% 	$\Sigma_e$ &state disturbance covariance matrix\\
% 	$\mathbf{\epsilon}_t$ & observation noise \\
% 	$\Sigma_{\epsilon}$ &observation noise covariance matrix\\
%     	$\mathbf{C}$ & observation matrix \\
% 	$c_{ij}$& elements of observation matrix
%     \end{tabular}
%     \caption{Decomposition}
% \end{table}
% 
% \begin{table}[h!]\footnotesize
%     \begin{tabular}{rl}
%         $V(\nu)$ & Spectrum of the dynamic field \\
% 	$\nu$ & Spatial frequency \\
% 	$\nu_c$ & Spatial cut-off frequency \\
% 	$\Delta_y$ & Distance between adjacent sensors \\
% 	$\rho$ & Over-sampling parameter \\
% 	$\Delta_{\phi}$ & Distance between field basis functions \\
% 	$\sigma_{\nu}^2$ & Variance of FT of Gaussian basis function \\
% 	$\sigma^2_{\phi}$ & Spatial variance of Gaussian in spatial domain \\
%     \end{tabular}
%     \caption{Frequency Analysis}
% \end{table}
% 
% \begin{table}[h!]\footnotesize
%     \begin{tabular}{ll}
%         $\hat{\mathbf{x}}$ & State estimate \\
% 	$\chi$ & Matrix of sigma vectors \\
% 	$\lambda$& Scaling parameter\\
% 	$\alpha$& Determines the spread of sigma points\\
% 	$\beta$& Prior knowledge of the sigma points distribution\\
% 	$\kappa$& Scaling parameter\\
% 	$W$& Sigma vecors weights\\
%     	$\hat{\mathbf{x}}_t^{f-}$ & Forward prior estimate \\
%     	$\hat{\mathbf{x}}_t^f$ & Forward posterior estimate \\
%     	$\hat{\mathbf{x}}_t^{b-}$ & Backward prior estimate \\
%     	$\hat{\mathbf{x}}_t^{b}$ & Backward posterior estimate \\
%     	$P^f_t$ & Forward posterior covariance matrix \\
%     	$P^{f-}_t$ & Forward prior covariance matrix \\
%     	$P^b_t$ & Backward posterior covariance matrix \\
%     	$P^{b-}_t$ & Backward prior covariance matrix \\
% 	$\mathcal K_{t} $& Filter gain\\
% 	$M_t$& Cross-covariance matrix\\
% 	$S_t$& Smoother gain
%     \end{tabular}
%     \caption{State Estimation}
% \end{table}

>>>>

\begin{table}[!ht]
\caption{
\bf{Notation and Parameters}}
\begin{tabular}{|c|c|c|c|}
	\hline
	\textbf{Symbol} & \textbf{Quantity} & \textbf{Value} & \textbf{Units}\\
	\hline
\multicolumn{4}{|c|}{\emph{Domain and indices}}\\
\hline
$\Omega$ & spatial domain & &\\
$t$ & time & & seconds\\
$\mathbf{r}$ & spatial location & &\\
$n$ & sensor index $n=1,..,N$ & &\\
$T_s$ & time step & $0.001$ & seconds\\
$T$ & number of time steps & 0.4 & seconds\\
\hline
\multicolumn{4}{|c|}{\emph{Spatiotemporal signals}}\\
\hline
    $y(\mathbf{r}_n,t)$ & observation & & mV\\
    $v(\mathbf{r},t)$ & mean membrane potential & & mV \\
	$g(\mathbf{r},t)$ & weighted firing rate function & & \\
	$f(\mathbf{r},t)$ & firing rate function & & spikes.s$^{-1}$\\
	$e(\mathbf{r},t)$ & field disturbance, (covariance $\gamma$) & &\\
	$\varepsilon(\mathbf{r}_n,t)$ & observation noise, (covariance $\Sigma_\epsilon$) & &\\
\end{tabular}
\begin{flushleft}Table caption
\end{flushleft}
\label{tab:label}
\end{table}

% ~~~~~~~~~~~~~~~~~~~~

% 
% \begin{table}[h!]\footnotesize
%     \begin{tabular}{ll}
%         	$h(t)$ & post-synaptic response kernel \\
% 	$m(\mathbf{r},\mathbf{r}')$ & sensor kernel, width $\sigma_m^2$ \\
% 	$\eta(t)$ & Heaviside function \\
% 	$\zeta$ & inverse synaptic time constant \\
% 	$w(\mathbf{r},\mathbf{r}')$ & spatial connectivity kernel \\
% 	$f_{max}$ & maximal firing rate \\
% 	$\varsigma$ & slope of sigmoidal activation function \\
% 	$v_0$ & firing threshold \\
% 	$\delta(t)$ & Dirac-delta function \\
% 	$D$ & Temporal differential operator \\
% 	$\xi$ & time constant parameter
%     \end{tabular}
%     \caption{Model}
% \end{table}
% 
% \begin{table}[h!]\footnotesize
%     \begin{tabular}{ll}
%         $L$ & number of field basis functions  \\
%     	$\mathbf{\phi(r)}$ & vector of Gaussian basis functions \\
%     	$\mathbf{x}_t$ & state vector at time $t$ \\
%     	$\mathbf{\psi}$ & vector of connectivity kernel basis functions \\
%     	$\theta$ & vector of connectivity kernel parameters \\
%     	$\Gamma$ & inner product of field basis functions \\
%     	$q()$ & state function \\
%     	$Q()$ & state function \\
% 	$\gamma(\mathbf r-\mathbf r')$& field disturbance covariance function\\
%     	$\mathbf{e}_t$ & state disturbance \\
% 	$\Sigma_e$ &state disturbance covariance matrix\\
% 	$\mathbf{\epsilon}_t$ & observation noise \\
% 	$\Sigma_{\epsilon}$ &observation noise covariance matrix\\
%     	$\mathbf{C}$ & observation matrix \\
% 	$c_{ij}$& elements of observation matrix
%     \end{tabular}
%     \caption{Decomposition}
% \end{table}
% 
% \begin{table}[h!]\footnotesize
%     \begin{tabular}{rl}
%         $V(\nu)$ & Spectrum of the dynamic field \\
% 	$\nu$ & Spatial frequency \\
% 	$\nu_c$ & Spatial cut-off frequency \\
% 	$\Delta_y$ & Distance between adjacent sensors \\
% 	$\rho$ & Over-sampling parameter \\
% 	$\Delta_{\phi}$ & Distance between field basis functions \\
% 	$\sigma_{\nu}^2$ & Variance of FT of Gaussian basis function \\
% 	$\sigma^2_{\phi}$ & Spatial variance of Gaussian in spatial domain \\
%     \end{tabular}
%     \caption{Frequency Analysis}
% \end{table}
% 
% \begin{table}[h!]\footnotesize
%     \begin{tabular}{ll}
%         $\hat{\mathbf{x}}$ & State estimate \\
% 	$\chi$ & Matrix of sigma vectors \\
% 	$\lambda$& Scaling parameter\\
% 	$\alpha$& Determines the spread of sigma points\\
% 	$\beta$& Prior knowledge of the sigma points distribution\\
% 	$\kappa$& Scaling parameter\\
% 	$W$& Sigma vecors weights\\
%     	$\hat{\mathbf{x}}_t^{f-}$ & Forward prior estimate \\
%     	$\hat{\mathbf{x}}_t^f$ & Forward posterior estimate \\
%     	$\hat{\mathbf{x}}_t^{b-}$ & Backward prior estimate \\
%     	$\hat{\mathbf{x}}_t^{b}$ & Backward posterior estimate \\
%     	$P^f_t$ & Forward posterior covariance matrix \\
%     	$P^{f-}_t$ & Forward prior covariance matrix \\
%     	$P^b_t$ & Backward posterior covariance matrix \\
%     	$P^{b-}_t$ & Backward prior covariance matrix \\
% 	$\mathcal K_{t} $& Filter gain\\
% 	$M_t$& Cross-covariance matrix\\
% 	$S_t$& Smoother gain
%     \end{tabular}
%     \caption{State Estimation}
% \end{table}
